<!-- View Preview: Ctrl-K-V -->

---
title: "Data Science SoSe 2014: Einsendeaufgabe 4"
author: "Alexander Gayko, TH Brandenburg" 
date: "2024-05-12"
output: html_document
---

# Introduction
- Note: I'm working in VS Code, because i don't want to install RStudio.

## Botanical Context: 
- Sepal - Kelchblatt
- Petal - Blütenblatt
- Iris Setosa - Borstenschwertlilie
- Iris Virginica - Blaue Sumpfschwertlilie
- Iris Versicolor - Schillernde Schwertlilie

# Assignment:

## Preparations
1. Download Rstudio & R
2. Use Rstudio(Posit) to create rmarkdown file
3. Running the following analysis from Rmarkdown

### Configuration
- download package ggplot2
```{r}
#install.packages("ggplot2")
library(ggplot2)
```
- import the data("iris")
```{r}
data("iris")
# head(iris) # Anzeigen der ersten Paar Zeilen
```
- use the ggplot for all the tasks below

## Scatter Plot
- make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  ggtitle("Scatterplot: Width over Length") +
  geom_point()
```

## Scatterplot with regression lines
- add regression line for the previous plot with the whole dataset (regardless of the species)
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  ggtitle("Scatterplot: Width over Length with Regression lines") +
  geom_point() +
  geom_smooth(method = "lm")
```

## Pearson Correlation
- calculate the Pearson correlation for this plot
```{r}
cor.test(iris$Sepal.Width, iris$Sepal.Length,
         method = "pearson")
# pearson is the default method, so that parameter is optional
```

### Conclusion
The Pearson correlation coefficient of -0.1175698 indicates a weak negative corellation between the sepal's length and width.
This is to be expected, since sepals are naturally grown objects which need a certain width to support their length without breaking.

## Box Plot
- make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors
```{r}
ggplot(iris, aes(y = Species, x = Petal.Width, color = Species)) +
  ggtitle("Boxplots Species vs. Petal Width") +
  geom_point() +
  geom_boxplot()
```

## Histogram
- make the histogram for Petal.Width with 3 species separately in x-axis in different colors
```{r}
ggplot(iris, aes(x = Petal.Width, color = Species)) +
  ggtitle("Histogram: Petal Widths") +
  geom_histogram(binwidth = 0.05)

```

## T-Test
- run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species
```{r}
t.test(Petal.Width ~ Species, data = iris,
       subset = Species %in% c("setosa", "virginica"))
```
<!--
### Result
`
        Welch Two Sample t-test

data:  Petal.Width by Species
t = -42.786, df = 63.123, p-value < 2.2e-16
alternative hypothesis: true difference in means between group setosa and group virginica is not equal to 0
95 percent confidence interval:
 -1.863133 -1.696867
sample estimates:
   mean in group setosa mean in group virginica
                  0.246                   2.026 
`
-->

### Conclusion
- The p-value of 0.00000000000000022 is far less than 0.05, so we can reject the null hypothesis, and conclude that the Petal.Width is a statistically significant difference between setosa and virginica
- This StackExchange answer proposes that that value is actually a placeholder for an even smaller value, output by R when the p-value is too small to be represented in floating point arithmetic: https://stats.stackexchange.com/a/403369

## Submission
4. knit to html

- You need to submit 2 files, one is the .Rmd file and the other is .html file
- The github/Gitlab link is acceptable as well.
